---
title: "Nate Harrington WHYY"
output: html_document
date: "2025-05-5"
---

A demo notebook for Dow Jones News Fund data interns

During the week’s training, you will work on a project called Investigate Your Community to produce detailed story pitches relevant to their summer internship positions. The goal is to have the students research a topic relevant to your newsroom so they can get to work immediately at the internship. 

Here are some examples from last year’s DJNF data journalism training:

Hannah Rosenberger, at ASI Media/Counselor magazine, produced this analysis on name, image and likeness trends: https://hrosenberger.github.io/ASI-NIL-Project/

Shifra Dayak, an intern at the Connecticut Mirror, produced this analysis of environment spill data: https://shifradayak.github.io/DJNF_Merrill/ct_env_spills.html.

Michael Zhang, an intern at the Houston Landing, explored local election data: https://michaelzhangreporter.github.io/Houston_Campaign_Finance/


Here's what your newsroom suggested for a project
Here are some newsroom-wide projects coming up that we welcome data journalism contributions from our future DJ interns.
 
Aging in the region – tentative project title is “Growing Golden: Aging with Purpose.” Numerous stories about aging and thriving in retirement will cover a range of financial, health, housing, dying, family coping and planning for retirement story topics. This is an explanatory journalism project.
 
Developing project on Black Women in the region – inspired by the election of Philadelphia’s first woman mayor and Black woman mayor. Areas of storytelling will include: politics, education and health
 
Philadelphia neighborhood guides is a project coming from Billy Penn.
 
An existing project on education is such, and we will continue to produce stories through mid-summer -- Creativity Sparks Success Project https://whyy.org/series/creativity-sparks-success/



This notebook helps you get started on the Growing Golden project.


# Load software libraries
```{r}
#install.packages("tidyverse")
#install.packages("janitor")
#install.packages("readxl")
#install.packages("rvest")
library(tidyverse)
library(janitor)
library(readxl)
library(rvest)

```


# Load your data

Check Census Reporter for ideas. Here's a start
https://censusreporter.org/data/table/?table=B01001&primary_geo_id=16000US4260000&geo_ids=16000US4260000,05000US42101,31000US37980,04000US42,01000US


```{r}

# 
# YOUR_DATA <- read.csv("../data/XXXXX.csv") |> 
#     clean_names()

# data <- read_excel("../data/2024-12-Revenue.xlsx", skip=2) |> 
#     clean_names()

data <- read.csv("../data/acs2023_1yr_B01001_04000US42.csv") |> 
    clean_names() 
```

Restructure the table for 

```{r}


demographic_table <- data %>%
  # First select just the relevant columns
  select(name, starts_with("b01001")) %>%
  # Pivot to make each b01001 variable a row
  pivot_longer(cols = starts_with("b01001"),
               names_to = "variable",
               values_to = "value") %>%
  # Then pivot to make each location a column
  pivot_wider(names_from = name,
              values_from = value) %>%
  # Clean up column names if needed
  rename_with(~ gsub(", PA$", "", .x), matches("Philadelphia County")) %>%
  rename_with(~ gsub(" Metro Area$", "", .x), matches("Philadelphia-Camden")) |> 
  clean_names()

```

Data details:


# Explore the data types
```{r}

#glimpse(YOUR_DATA)

glimpse(data)

```
# Fix dates
```{r}
data <- data |> 
  mutate(date = lubridate::mdy(contribution_date))
```



# Data exploration: dates

```{r}
data |> 
   count(date) |> 
  arrange(desc(n))
```




# Questions 

Write down questions you want answered:



# Data Details
